Mutual Modelling

### 2015-06-17 mutual-modeling.tex
Updated title + list of authors

\title{Do I Need to Model You in order to Learn With You?}
\subtitle{Mutual Modelling in CSCL}

\author{
    Pierre Dillenbourg
    \and
    Séverin Lemaignan
    \and
    Mirweis Sangin
    \and
    Nicolas Nova
    \and
    René Glaus
    \and
    Gaëlle Molinari
}
\institute{
    Pierre Dillenbourg, Séverin Lemaignan \at Computer-Human Interaction in Learning and Instruction \\
    École Polytechnique Fédérale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
    \email{firstname.lastname@epfl.ch}
    \and
    Mirweis Sangin \at Sony Computer Entertainment Europe
    \and
    Nicolas Nova \at Haute École Arts \& Design de Genève \\\email{nicolas.nova@hesge.ch}
    \and
    René Glaus
    \and
    Gaëlle Molinari \at Fernuni Schweiz \\\email{gaelle.molinari@fernuni.ch}
}
\begin{document}
\maketitle

@@

The experiments were developed with the help of Patrick Jermann,  Fabien
Girardin, Marc-Antoine Nüssli, Thomas Werhle, Yvan Bourquin and  Jeremy Goslin.
The main funding has been provided from a NSF Grant grant \#102511-106940.

>>>>

\title{Mutual Modelling}

\author{
    Pierre Dillenbourg
    \and
    Séverin Lemaignan
    \and
    Nicolas Nova
    \and
    Gaëlle Molinari
}
\institute{
    Pierre Dillenbourg, Séverin Lemaignan \at Computer-Human Interaction in Learning and Instruction \\
    École Polytechnique Fédérale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
    \email{firstname.lastname@epfl.ch}
    \and
    Nicolas Nova \at Haute École Arts \& Design de Genève \\ CH-1201 Genève, Switzerland\\\email{nicolas.nova@hesge.ch}
    \and
    Gaëlle Molinari \at Distance Learning University Switzerland (Unidistance),
    CH-3960 Sierre, Switzerland\\\email{gaelle.molinari@unidistance.ch}
}
\begin{document}
\maketitle

@@

The experiments were developed with the help of Mirweis Sangin, René Glaus,
Patrick Jermann,  Fabien Girardin, Marc-Antoine Nüssli, Thomas Werhle, Yvan
Bourquin and Jeremy Goslin.  We also thank Kshitij Sharma and {\L}ukasz
Kidzi\'nski for their help with data analysis. The main funding has been
provided from a NSF Grant grant \#102511-106940.
